---
title: "Schedule"
---

```{r}
#| include: false
knitr::opts_chunk$set(echo = FALSE)
```

```{r}
#| message: false
#| warning: false
library(tidyverse)
library(bsplus)
library(fontawesome)
library(htmltools)
library(RefManageR)
library(lubridate)
library(calendR)

bib <- ReadBib("DataEthnography.bib")

topics <- read.csv("data/topics.csv") %>%
  mutate(date = mdy(date)) %>%
  arrange(date)
standards <- read.csv("data/standards.csv") %>%
  mutate(standard_id = as.character(standard_id))
topics[topics == ""] <- NA
standards[standards == ""] <- NA
required_reading <- topics %>%
  select(topic_abbr, required_reading, req_chapter) %>%
  separate_rows(required_reading, req_chapter, sep = ";") %>%
  rename(reading = required_reading,
         chapter = req_chapter)
optional_reading <- topics %>%
  select(topic_abbr, optional_reading, opt_chapter) %>%
  separate_rows(optional_reading, opt_chapter, sep = ";") %>%
  rename(reading = optional_reading,
         chapter = opt_chapter)
writing_assignments <- topics %>%
  select(topic_abbr, writing_assignment) %>%
  separate_rows(writing_assignment, sep = ";")
project_assignments <- topics %>%
  select(topic_abbr, project_assignment) %>%
  separate_rows(project_assignment, sep = ";")
topic_standards <- 
  topics %>%
  select(topic_id,topic_abbr,topic,standard_id,date) %>%
  separate_rows(standard_id, sep = ";") %>%
  left_join(standards)
slides <- 
  topics %>%
  select(topic_abbr, slides) %>%
  separate_rows(slides, sep = ";")
links <- 
  topics %>%
  select(topic_abbr, link) %>%
  separate_rows(link, sep = ";")
codes <- 
  topics %>%
  select(topic_abbr, code) %>%
  separate_rows(code, sep = ";")
```

```{r}
#| include: false
source("R/print_assignments.R", local = knitr::knit_global())
source("R/buttons.R", local = knitr::knit_global())
source("R/calendar.R", local = knitr::knit_global())
#source("css/custom.css", local = knitr::knit_global())
```

::: callout-note
## Acknowledgements

Styling and infrastructure for this page inspired by [related syllabi](https://beanumber.github.io/sds192/schedule.html) produced by Ben Baumer and R. Jordan Crouser.
:::

::: callout-tip
All readings for this course will be available in our course Perusall, which is linked in Moodle. I encourage you to complete the readings there so that you can leave comments and questions as they come up.
:::

:::{.callout-note collapse="true"}

## Calendar View for Major Assignments

```{r message=FALSE, warning=FALSE, results='hide', fig.keep='all'}
annotation_due_dates <- topics %>%
  select(date, required_reading) %>%
  separate_rows(required_reading, sep = ";") %>%
  filter(required_reading != "") %>%
  mutate(month = month(date), day = day(date))

written_due <- topics %>%
  select(date, assignment = writing_assignment) %>%
  separate_rows(assignment, sep = ";")

group_due <- topics %>%
  select(date, assignment = project_assignment) %>%
  separate_rows(assignment, sep = ";") 

major_due_dates <- rbind(written_due, group_due) %>%
  filter(str_detect(assignment, "Due")) %>%
  mutate(month = month(date), day = day(date)) %>%
  group_by(date, month, day) %>%
  summarize(assignment = paste(assignment, collapse = '\n'))

for(i in unique(major_due_dates$month)){
  print_calendar(major_due_dates, annotation_due_dates, i)
}
```

:::

```{r}
#| message: false
#| results: 'asis'
for (i in 1:nrow(topics)){
  
  todays_topic <- topics %>%
    slice(i)
  
  date_format <- stamp("January 17, 1999")
  
  cat(paste("## ", date_format(ymd(todays_topic$date[1]))))
  cat("\n")
  cat(paste("### ", todays_topic$topic[1]))
  cat("\n")
  print_this_week_standards_buttons(todays_topic$topic_abbr[1])
  cat("\n")
  cat("\n")
  cat("::: {.panel-tabset}")
  cat("\n")
  cat("#### Due Today")
  cat("\n")
  BibOptions(check.entries = FALSE,
           bib.style = "authoryear", 
           style = "html",
           dashed = TRUE,
           first.inits = FALSE, 
           no.print.fields = c("url", "doi", "issn"))
  print_due_today(todays_topic$topic_abbr[1])
  cat("\n")
  cat("#### Further Resources")
  cat("\n")
  print_further_reading(todays_topic$topic_abbr[1])
  cat("\n")
  cat(":::")
  cat("\n")
}
```
