---
title: "Day Twenty: Ethnographic Arguments"
subtitle: "SDS 237: Data Ethnography"
author: |
  Lindsay Poirier<br/>
  <span style = 'font-size: 70%;'>
  [Statistical & Data Sciences](http://www.smith.edu/sds), Smith College<br/>
  </span>
date: |
  Spring 2022<br/>
  `r sds::img_logo(width = 64)`
output:
  sds::moon_reader:
    lib_dir: libs
    css: xaringan-custom.css
    nature:
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
---

```{r setup, include=FALSE}
options(htmltools.dir.version = FALSE)
```

```{r xaringan-themer, include=FALSE}
# sds::duo_smith()
sds::mono_light_smith()
```

# Announcements

* Stay tuned for updates about Monday's class

---

# What is an ethnographic argument?

* Central theme derived from an ethnographic study
* Identifies a certain cultural pattern or phenomena
* Examples:
  * How data is talked about
  * The cultural assumptions underpinning a data infrastructure
  * How labor is recognized in a data practice

---

# Writing an Ethnographic Argument

* Paragraph 1: Introduction and thesis
* Paragraph 2-x: Sub-arguments supporting thesis
  * Presents evidence from data collection to support sub-argument
* Paragraph Final: Summarize thesis and wrap-up

---

# What counts as evidence/data in ethnographic arguments?

* Discourse Analysis/Interview
  * Direct quotes and their context
* Participant Observation
  * Vignettes/thick description
* Cultural Analysis of Infrastructure
  * Material from secondary sources
  * Facts about the infrastructure's historical development
  * Descriptions of the organization of the infrastructure
  
---

# Revision Expectations

* Revision = re - vision = seeing again
* Involves more than spelling and grammar fixes and word changes; editing is only one component of revision
* Things to consider:
  * Recognize and re-articulate the purpose
  * Refine the focus (audience and presentation)
  * Clarify the argument
  * Strengthen and hone evidence

> [https://writingcenter.unc.edu/tips-and-tools/revising-drafts/](https://writingcenter.unc.edu/tips-and-tools/revising-drafts/ )